### 2023-12-31 docs/projects/data-formats/hdf/index.qmd
rerendered hdf project

<div><pre><small><small>source: /home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</small></small></pre></div>

>>>>

<div><pre><small><small>source: <a href="https://github.com/scicloj/clojure-data-scrapbook/blob/main//home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj">/home/daslu/projects/scicloj/clojure-data-scrapbook/projects/data-formats/hdf/notebooks/index.clj</a></small></small></pre></div>
